\section{Tuples}

Tuples are simply lists of
\begin{itemize}
	\item Expressions
	\item Bindings.
	\item If statments (Without else).
\end{itemize}

\noindent Tuples follows the following rules
\begin{itemize}
	\item If the expression is followed by the seperator \texttt{,} then the
	      expression is non-vanishing, that is its value is evaluated, and is
	      is an entry in the final tuple.

    \item If the expression is is followed by the seperator \texttt{;} then
        the expression is vanishing, that is its value is evaluated, and its
        not an entry in the final tuple.

    \item If the last item is not followed by a seperator, then it is treated
        as a non-vanishing entry.

    \item If the tuple is empty then its a vanishing entry regardless of the
        following seperater.

        \item If the tuple entry is a direct predicate call then it has
            a special behavior: if the predicate call evaluates to
            true, then the execution of function will continue as it its,
            otherwise it the function will fail(like in regular predicates).

            Regardeless of the predicate call result, the predicate call's 
            entry in the tuple is \textbf{always} vanishing.
\end{itemize}

Tuples are compiled to the predicate \texttt{tuple(...)} when
\texttt{...} are the non-vanishing entries of the tuple.

\subsection{Examples}
\begin{enumerate}
	\item \texttt{(1,2)}.
	\item \texttt{([3,4],Max(4,3),(1,2))}, evalutes to \texttt{tuple([3,4],Max(4,3),(1,2))}.
	\item \texttt{([3,4];Max(4,3),(1,2);)}, evalutes to \texttt{tuple(Max(4,3),(1,2))}.
\end{enumerate}

\begin{note}
	The number of entries in the tuple's predicate is determined at compile time, for this reason,
	an if statement (Without else) can only be a vanishing statement.
\end{note}

